%====================== APPLE INSPIRED RESUME ======================%

\documentclass[letterpaper,10pt]{article}

% Typography & Layout
\usepackage[sfdefault]{sourcesanspro}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{SectionGray}{RGB}{60,60,60}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{fancyhdr}

% Page formatting
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1.05in}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section title style
\titleformat{\section}{
  \vspace{-4pt}\color{SectionGray}\scshape\raggedright\large
}{}{0em}{}[\color{SectionGray}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\gray}[1]{\textcolor{SectionGray}{#1}}
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{0pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%===================== DOCUMENT BEGINS =====================%
\begin{document}

%-------------------- HEADER --------------------%
\begin{center}
    {\LARGE \textbf{Chinmay Rozekar}} \\[3pt]
    \small Hillsboro, OR \,|\, 
    \href{mailto:chinmay.rozekar@gmail.com}{chinmay.rozekar@gmail.com} \,|\, 
    \href{https://linkedin.com/in/chinmayrozekar}{linkedin.com/in/chinmayrozekar} \,|\, 
    \href{https://github.com/chinmayrozekar}{github.com/chinmayrozekar} \\[4pt]
    \small \textit{Lead QA Engineer \,\,\textperiodcentered\,\, Automation Strategy \,\,\textperiodcentered\,\, Python \,\,\textperiodcentered\,\, CI/CD \,\,\textperiodcentered\,\, Cloud and Desktop Testing}
\end{center}

%-------------------- PROFILE --------------------%
\section*{\gray{Profile}}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
Lead-level QA engineer with 6 years of experience designing automation frameworks, defining validation strategy, and enabling cross-team quality processes across semiconductor and software domains. Skilled in Python, CI/CD, and test infrastructure for complex desktop and cloud environments. Known for data-driven quality metrics, reproducible pipelines, and mentoring engineers to accelerate release readiness.
}}
\end{itemize}

%-------------------- TECHNICAL SKILLS --------------------%
\section*{\gray{Technical Skills}}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} Python, Tcl, Bash, Perl, C/C++, SQL \\
\textbf{Automation and QA:} Test framework design, regression infrastructure, API and functional testing, KPI dashboards \\
\textbf{Tools:} Jenkins, Docker, Git, Jira, Confluence, Power BI, Siemens Calibre PERC, DRC/LVS \\
\textbf{Domains:} Desktop application testing, cloud automation, reliability verification, post-silicon validation \\
\textbf{OS:} Linux (RHEL/SLES), macOS, Windows
}}
\end{itemize}

%-------------------- EXPERIENCE --------------------%
\section*{\gray{Experience}}
\resumeSubHeadingListStart

\resumeSubheading{Software QA Engineer \,\, Calibre PERC}{2024 -- 2025}{Siemens EDA (Mentor Graphics)}{Wilsonville, OR}
\resumeItemListStart
  \resumeItem{Led QA automation for the Calibre PERC reliability verification platform, guiding strategy for ESD, EOS, and multi-voltage validation flows used by global design teams.}
  \resumeItem{Developed Python and Tcl pipelines for nightly regression and configuration checks, reducing setup time by 20 percent and improving stability by 15 percent.}
  \resumeItem{Collaborated with R\&D and CAD groups to align rule sequencing QA and electrical topology coverage across hierarchical SoC designs.}
  \resumeItem{Built Power BI dashboards tracking runtime and defect metrics to support data-driven release decisions and improve visibility across teams.}
  \resumeItem{Authored QA runbooks and onboarding documentation that reduced new engineer ramp-up time by 30 percent and standardized validation procedures.}
\resumeItemListEnd

\resumeSubheading{System Level Test Engineer \,\, Product Development}{2019 -- 2024}{Advanced Micro Devices (AMD)}{Austin, TX}
\resumeItemListStart
  \resumeItem{Owned post-silicon validation for Ryzen 8040 APU SoCs across 14 IP blocks to ensure functional, power, and reliability qualification before production.}
  \resumeItem{Automated data capture and yield analysis in Python and Perl, reducing manual debug effort by 40 percent and improving correlation accuracy across lots.}
  \resumeItem{Developed Power BI dashboards for real-time KPI visualization and triage tracking that shortened defect turnaround by 25 percent.}
  \resumeItem{Mentored junior engineers on test data pipelines and analysis tools and standardized debug processes across multiple teams.}
  \resumeItem{Collaborated with firmware and diagnostics teams to reproduce and resolve BIOS and system-level failures during qualification.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- PROJECTS --------------------%
\section*{\gray{Selected Projects}}
\resumeSubHeadingListStart

\resumeItem{\textbf{HelmNet \,\, AI Safety Helmet Detection}}
\resumeItemListStart
  \resumeItem{Developed a VGG16 transfer learning model to detect PPE compliance in industrial images with 91.8 percent validation accuracy and 0.92 F1-score. Deployed with Streamlit and Docker for real-time use.}
\resumeItemListEnd

\resumeItem{\textbf{SuperKart \,\, Retail Forecasting Workflow}}
\resumeItemListStart
  \resumeItem{Built a Gradient Boosting forecasting model on 8{,}763 transactions achieving $R^{2}=0.86$ and MAE $=0.43$ and deployed via a Dockerized Flask API with a dashboard for cloud prediction.}
\resumeItemListEnd

\resumeItem{\textbf{RAG-based Medical Assistant}}
\resumeItemListStart
  \resumeItem{Implemented a Retrieval Augmented Generation system using Mistral-7B and ChromaDB on a 4000 page medical corpus that improved retrieval accuracy by 23 percent versus baseline search.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- EDUCATION --------------------%
\section*{\gray{Education}}
\resumeSubHeadingListStart
\resumeSubheading{University of Texas at Austin}{2025}{Post Graduate Program in Artificial Intelligence and Machine Learning}{Online}
\resumeSubheading{Rochester Institute of Technology}{2020}{Master of Science, Electrical Engineering}{Rochester, NY}
\resumeSubheading{Bharati Vidyapeeth University}{2016}{Bachelor of Technology, Electrical Engineering}{Pune, India}
\resumeSubHeadingListEnd

\end{document}