\documentclass[10pt]{letter}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{charter}
\usepackage{setspace}
\usepackage{parskip}
\setstretch{1.2}

\begin{document}

\begin{letter}{Hiring Manager}

\opening{Dear Hiring Manager,}

I am writing to express my interest in engineering roles related to semiconductor validation, EDA enablement, or design infrastructure development. Over the past five years, I have worked across both silicon validation and EDA QA automation, combining hands-on system-level experience at AMD with software validation expertise at Siemens EDA. This combination has given me a strong technical foundation and a practical understanding of how design, verification, and enablement teams work together to deliver reliable semiconductor products.

At \textbf{Siemens EDA}, I validate Calibre PERC features used for reliability verification, including ESD, EOS, and topology-based analysis. I create regression suites using SVRF, automate test execution and log analysis using Python and Tcl, and collaborate directly with developers to identify and fix rule-sequencing and runtime issues. My work ensures deterministic sign-off behavior, improved runtime performance, and consistent validation coverage across feature releases. Through these efforts, I have contributed to product readiness and customer confidence in sign-off verification flows.

Before joining Siemens, I worked at \textbf{Advanced Micro Devices (AMD)} as a System-Level Test Engineer, responsible for SoC bring-up, device characterization, and post-silicon validation across multiple IPs. I developed and deployed production-level test programs for IR drop, voltage drop, and reliability characterization, managed large-volume test operations, and performed data-driven yield analysis. I also collaborated closely with BIOS, memory, and board design teams to debug hardware and improve bring-up success rates. This experience helped me develop a deep understanding of silicon behavior, production test environments, and the importance of tool and flow reliability in enabling product success.

I am particularly drawn to roles that combine technical depth, process optimization, and cross-functional collaboration. My experience across the EDA and silicon validation domains allows me to bridge product development, test automation, and customer success initiatives. I am confident that my background in both verification software and SoC hardware validation can bring valuable perspective to any team focused on engineering enablement, product readiness, or EDA infrastructure improvement.

Thank you for taking the time to review my application. I would welcome the opportunity to discuss how my experience and approach to problem solving can contribute to your organization’s success.

\closing{Sincerely, \\[0.5em]
\textbf{Chinmay Rozekar} \\[0.2em]
Wilsonville, OR \\
\texttt{chinmay.rozekar@gmail.com}}

\end{letter}

\end{document}
