%-------------------------
% Resume in Latex
% Author : 
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING----------
	% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
		%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
		% \end{tabular*}
	
	%	\begin{center}
		%		\textbf{\Huge \scshape Jake Ryan} \\ \vspace{1pt}
		%		\small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{jake@su.edu}} $|$ 
		%		\href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
		%		\href{https://github.com/...}{\underline{github.com/jake}}
		%	\end{center}
	
	\begin{center}
		\textbf{\Huge \scshape Chinmay Rozekar} \\ \vspace{1pt}
		\small 646-510-5699 $|$ {chinmay.rozekar@gmail.com} $|$ 
		\href{https://linkedin.com/in/...}{{Austin,TX 78744}} 
		
	\end{center}
	
	
	%-----------OBJECTIVE-----------
	
	\section{Objective}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\vspace{-10pt}
		
		\def\objective{Accomplished Electrical Engineer with over 4 years of experience in Silicon Validation and MEMS, ready to apply a deep understanding of electrical control systems, system-level testing, and product development to innovative equipment design as an Electrical Engineer 5 at Lam Research.}
		
		
		
		
		
		
		\item \resumeItem{\objective}
	\end{itemize}
	\vspace{-15pt}
	
	
	\section{Professional Summary}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\resumeSubSubheading{}{}
		\resumeItemListStart
		\vspace{-15pt}
		\resumeItem{Versatile engineer with 4+ years in Silicon Validation, adept in both Pre-Silicon and Post-Silicon environments, specializing in system-level testing and product quality enhancement.}
		\resumeItem{Committed to leveraging technical expertise for reducing operational costs and enhancing product specifications.}
		\resumeItem{Excels in cross-functional team collaboration, test automation with Python, C/C++, and Java, and innovative problem-solving.}
		% \resumeItem{Seeks a dynamic engineering role to apply a broad skill set in Silicon Validation and Hardware Engineering.}
		\resumeItemListEnd
	\end{itemize}
	\vspace{-15pt}
	
	
	
	%-----------EXPERIENCE-----------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Product Development Engineer}{July 2020 -- Present}
	{Advanced Micro Devices (AMD)}{Austin, TX}
	%\vspace{-9pt}
	\resumeSubSubheading{System Level Testing (SLT)}{}
	\resumeItemListStart
	\resumeItem{Led system-level testing for AMD's Ryzen 8040 'Hawkpoint' series, Accelerated Processing Units (APUs), ensuring adherence to customer environment standards.}
	
	\resumeItem{Spearheaded Test Time Reduction (TTR), eliminated redundant tests, for reducing operational costs through DPPM Yield Analysis in Production.}
	\resumeItem{Experienced in monitoring production yield and debugging/root cause analysis of high-Pareto items in production fallout.}
	\resumeItem{Experienced in performing SoC Characterization for Product Definition by setting Test-Program flows on volume testing. }
	
	\resumeItem{Maintained the test program codebase repository using Atlassian BitBucket, overseeing the development and release of test content throughout the product roadmap.}
	\resumeItem{Collaborated with Diagnostic, BIOS, and Design teams to enhance CPU performance features, contributing to product specification improvements.}
	\resumeItem{Experienced in Customer RMA Debug issues through secure fuse unlocking during Field Return Analysis (FRA).}
	\resumeItem{Established and managed an in-house server farm and APU client board setup, ensuring robust testing environments and streamlining development.}
	
	
	
	
	
	
	
	\resumeItemListEnd
	
	
	
	\resumeSubheading
	{Product Engineering Co-Op}{Jan. 2019 -- Dec.2019}
	{Advanced Micro Devices (AMD)}{Austin, TX}
	\resumeItemListStart
	\resumeItem{Designed and automated test programs for Human Body Model Testing, reducing Engineering time by 90\%.}
	\resumeItem{Reverse-engineered and redesigned a 20-year-old robotic graphical user interface in Python, reducing engineering time by 95\%.}
	\resumeItem{Conducted stress tests on AMD products according to industry standards, qualifying products for production.}
	\resumeItem{Performed scheduled calibration and waveform verification for preventive maintenance as per ISO 9000 standards}
	\resumeItem{Conducted Design of Experiments on AMD products for Capacitive Modeling to optimize protection circuitry}
	\resumeItemListEnd
	
	\resumeSubheading
	{Graduate Research Assistant}{Jan 2020 -- May 2020}
	{Rochester Institute of technology}{Rochester, NY}
	\resumeItemListStart
	\resumeItem{Developed a process flow for thin film IC development, covering various fabrication steps}
	\resumeItem{Designed and simulated NMOS devices to determine sub-threshold voltages and model leakage current}
	\resumeItem{Conducted electrical device characterization to optimize gate oxide thickness on NMOS devices.}
	
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	\vspace{-15pt}
	
	%
	%-----------Technical  SKILLS-----------
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
				\textbf{Process Engineering}{: Thin Films, PVD, CVD, Sputtering, Dry Etch, Metrology, Characterization} \\
				\textbf{Languages}{: Java, Python, BASH, C/C++, SQL, HTML/CSS, XML, Markdown, MATLAB, Perl} \\
				\textbf{Libraries}{: Matplotlib, Pandas, Numpy, Scikit-learn, Selenium} \\
				\textbf{Developer Tools}{: Git, Jira, Confluence, Linux, CI/CD, IntelliJ Idea, VS Code, PyCharm, Eclipse, Jupyter, Anaconda, JSON, Notepad++, LaTeX} \\
				\textbf{Protocols}{: JTAG, PCIE, DFT, Boundry SCAN, ATPG} \\
				\textbf{Simulation}{: KiCAD, SolidWorks, COMSOL Multiphysics, Silvaco-Athena, Pyxis(Mentor Graphics)} \\
				\textbf{Data Analysis}{: Excel, Power-BI, JMP, Python} \\
		}}
	\end{itemize}
	
	%-----------PROJECTS-----------
	\section{Projects}
	\resumeSubHeadingListStart
	
	\resumeProjectHeading
	{\textbf{Review of Thin Film Technologies for Flexible Electronics} }{Jan 2020 -- May. 2020}
	\resumeItemListStart
	\resumeItem{Designed a simulation model for growing a 1 µm layer of flexible crystalline Si substrate on top of Tungsten metal layer using SOI method in Silvaco Athena.}
	\resumeItemListEnd
	
	
	\resumeProjectHeading
	{\textbf{A Thermally actuated four-legged MEMS based Silicon Micro-robot} }{May 2018 -- Dec. 2018}
	\resumeItemListStart
	\resumeItem{Designed and fabricated a thermally actuated MEMS based Silicon micro-robot. Modeled design in CAD / Solidworks and Heat Transfer using COMSOL multi-physics FEA.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	
	
	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Rochester Institute of Technology}{Rochester, NY}
	{Master of Science, Electrical Engineering}{Aug. 2017 -- May 2020}
	\resumeSubheading
	{Bharati Vidyapeeth University}{Pune, India}
	{Bachelor of Technology, Electrical Engineering}{Aug. 2012 -- June 2016}
	\resumeSubHeadingListEnd
	
	
	
	
	%-------------------------------------------
\end{document}
